Distributional Regression Forests for Probabilistic Precipitation Forecasting in Complex Terrain

### 2018-10-19 pkg/disttree/inst/draft/rejoinder.Rnw
now using data from MapTyrol to plot topography
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2337 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 55a805b19e96c8f92ba57febb79c0e09cb46e517

# Preamble
library("sp")
library("raster")
library("ncdf4")
data(StationsTyrol, package = "RainTyrol")
data(MapTyrol, package = "RainTyrol")
# data(MapTyrol_border, package = "RainTyrol")
# Create SpatialPointsDataFrame from station list
sp <- SpatialPointsDataFrame(subset(StationsTyrol,
                                    select=c(lon,lat)),
                             data = subset(StationsTyrol,
                                           select = -c(lon,lat)),
                             proj4string = crs(MapTyrol$RasterLayer))

@@

# Loading and plotting regular_ll GFS topography
##gfs <- raster("gfs_topo.nc")
##gfs_resampled <- raster::resample(gfs, MapTyrol$RasterLayer)
raster::image(raster("gfs_topo.nc"), col = cols,
              main=NA, ylab = "Latitude", xlab = "Longitude",
              xlim = c(9.8,13.2), ylim = c(46.6, 47.87), zlim = zlim,
              xaxt = "n", yaxt = "n")
box()
plot(MapTyrol$SpatialPolygons, add = TRUE)
points(sp, pch = 19, cex = .5)
axis(side = 1, at = xat); axis(side = 4, at = yat)
mtext(side = 4, line = 2, cex = .8, "Latitude")

>>>>

# Preamble
library("sp")
library("raster")
#library("ncdf4")
data(StationsTyrol, package = "RainTyrol")
data(MapTyrol, package = "RainTyrol")
# data(MapTyrol_border, package = "RainTyrol")
# Create SpatialPointsDataFrame from station list
sp <- SpatialPointsDataFrame(subset(StationsTyrol,
                                    select=c(lon,lat)),
                             data = subset(StationsTyrol,
                                           select = -c(lon,lat)),
                             proj4string = crs(MapTyrol$RasterLayer))

@@

# Loading and plotting regular_ll GFS topography
##gfs <- raster("gfs_topo.nc")
##gfs_resampled <- raster::resample(gfs, MapTyrol$RasterLayer)
raster::image(MapTyrol$RasterLayerGFS, col = cols,
              main=NA, ylab = "Latitude", xlab = "Longitude",
              xlim = c(9.8,13.2), ylim = c(46.6, 47.87), zlim = zlim,
              xaxt = "n", yaxt = "n")
box()
plot(MapTyrol$SpatialPolygons, add = TRUE)
points(sp, pch = 19, cex = .5)
axis(side = 1, at = xat); axis(side = 4, at = yat)
mtext(side = 4, line = 2, cex = .8, "Latitude")
